### 2019-08-13 thesis.tex
*** empty log message ***

The fundamental questions of heliophysics start right in the Sun and the
magnetic dynamo processes involved in the generation and variability of
magnetic fields in the Sun, and how it determines the dynamics of the
11-year solar cycle of sunspots. The appearance of sunspots is a sign of
solar activity, characterized by solar flares and coronal mass ejections.

This enhanced flux of energetic particles and radiation have direct impact
in the \emph{space weather} around Earth, triggering geomagnetic storms
that

Inside the heliosphere, the Sun, the space environment around Earth and the
interplanetary medium are extensively explored by space probes.
%% say something about it

>>>>

% Investigations of the origin and behavior of the solar wind, energetic
% particles, and magnetic fields in the heliosphere and their interaction
% with Earth and other planets, as well as with the interstellar medium.
% Investigations of the physics of magnetospheres, including fundamental
% interactions of plasmas and particles with fields and waves, and coupling
% to the solar wind and ionospheres.
% Investigations of the physics of the terrestrial mesosphere, thermosphere,
% ionosphere, including the coupling of these phenomena to the lower atmosphere
% and magnetosphere.
The major questions being studied by the international heliophysics community
involve the solar dynamics, the origin and evolution of the solar wind,
energetic particles and magnetic fields, and how they interact with Earth,
other planetary bodies and the interstellar medium. % In the list below we
% highlight the most Ref. \cite{schrijver2009}. 
% are listed below:
\begin{itemize}
\item The magnetic dynamo processes involved in the generation and variability
  of magnetic fields in the Sun, and how it determines the dynamics of the
  11-year solar cycle of solar activity \cite{Charbonneau2005};
\item The role of magnetic reconnection in the coronal mass ejection process
  \cite{Qiu2005};
\item The coronal heating problem \cite{Vinas2000,PP14,Pezzi2017};
\item   
\end{itemize}

The heliophysics research, as expected by the very definition of the heliosphere,
involves the study of a rich diversity of plasma phenomena. 
% % The appearance of sunspots is a sign of
% % solar activity, characterized by solar flares and coronal mass ejections.

% This enhanced flux of energetic particles and radiation have direct impact
% in the \emph{space weather} around Earth, triggering geomagnetic storms
% that

% Inside the heliosphere, the Sun, the space environment around Earth and the
% interplanetary medium are extensively explored by space probes.
%% say something about it
